Latex Example, Pandoc Conversion

### 2020-04-09 _other/pandoc/fansample.tex
Tex etc updates
pandoc typo

% url package
\usepackage{hyperref}

@@

% Titling and Author
\title{Sandbox Testing Latex}
\author{Fan Wang (University of Houston)}
\date{\today}

@@

\begin{enumerate}
	\item \textit{run this for word to tex}: pandoc --bibliography=fansample.bib -o fansample.docx fansample.tex
\end{enumerate}

>>>>

% url package
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

@@

% Titling and Author
\title{Latex Example, Pandoc Conversion}
\author{Fan Wang (University of Houston)}
\date{\today}

@@

\begin{enumerate}
	\item \textit{run this for tex to word with bib}: pandoc --bibliography=fansample.bib -o fansample.docx fansample.tex
\end{enumerate}
